Transfer Learning in Visual and Relational Reasoning

### 2019-11-16 cvpr_submission/summary.tex
Commented 2 sentences in CLEVR section + 1 sentence in  summary to reduce space. Also reduced size of transfer taxonomy by 10%.
polish of summary

In this paper, through the introduction of a novel Memory-Augmented Neural Network model, SAMNet, we have quantified the impact of Transfer Learning in Visual Reasoning. Designed to learn to reason over sequences of frames (i.e., static images), SAMNet shows significant improvements, on the video reasoning dataset COG, over the corresponding baseline. Analysis of the results highlights the model's ability to operate independently of the number of frames and generalize to samples with higher complexity, characterized by longer sequences and more complex scenes. However, SAMNet can sporadically store spurious objects in the memory, despite its mechanisms. This doesn't prevent the model to produce accurate predictions.

We also introduce a new taxonomy of transfer learning for visual reasoning, articulated around three axes: feature transfer, temporal transfer and reasoning transfer. To highlight the robustness of this taxonomy, we realize an extensive set of experiments with SAMNet over two datasets: COG and CLEVR, a diagnostic dataset for Question Answering over static images. SAMNet demonstrates clear generalization capabilities along certain axes and, through the cautious use of finetuning, further advances performance in visual reasoning.

We hope these contributions can bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.

>>>>

In this paper we quantified the impact of Transfer Learning on Visual Reasoning. 
We have proposed a new taxonomy of transfer learning for Visual Reasoning, articulated around three axes: feature, temporal and reasoning transfer. 
We have also introduced a novel Memory-Augmented Neural Network model called SAMNet.
SAMNet, designed to learn to reason over sequences of frames, shows significant improvements over SOTA models on the COG dataset for Video Reasoning  and achieves comparable performances on the CLEVR dataset for Image Resoning.

Taking that as a starting point and leveraging on the proposed taxonomy, we  have conducted an extensive set of experiments, with focus on impact of transfer learning in areas that might be considered as higher-level reasoning.
SAMNet demonstrated very good generalization capabilities along certain axes and, through the cautious use of fine-tuning, we have managed to eleviate its performance even further.

Finally, we note that some of the proposed tasks (e.g. Train on all but \textit{t}) are complementary to the ones already well established in the literature, e.g. in taskonomy~\cite{zamir2018taskonomy}.
We hope these contributions will bolster new research directions to acutely apply transfer learning to areas in need of data and continue exploring the conceivable performance improvements.
